Standartox: Standardizing toxicity data

### 2020-04-10 article/tikz/standartox-organigram.tex
submission

\node (epa-ecotox) [ecotox, above of = ecotox-id, align=center, xshift = -3cm, yshift = 4cm] {\Large EPA ECOTOX\\\Large raw data};
\node (ecotox-id) [standartox, align = center] at (-3cm,0cm) {\Large Identifiers};

>>>>

\node (ecotox-id) [standartox, align = center] at (0cm,0cm) {\Large Identifiers};
\node (epa-ecotox) [ecotox, above of = ecotox-id, align=center, xshift = 0cm, yshift = 4cm] {\Large EPA ECOTOX\\\Large raw data};
